---
title: "NY_shooting_incidents"
output:
  pdf_document:
    latex_engine: xelatex
  html_document:
    df_print: paged
mainfont: NanumGothic
---



```{r library}
library(tidyverse)
library(lubridate)
library(ggplot2)
library(dlookr)
library(Hmisc)
library(caret)
```

```{r}
#data loading
data = read.csv('https://data.cityofnewyork.us/api/views/833y-fsy8/rows.csv?accessType=DOWNLOAD')

head(data)

```
```{r}
summary(data)

```
```{r}
diagnose(data)

```
```{r}
describe(data)
```
```{r}
#Convert to factor

data$BORO <- as.factor(data$BORO)
data$PRECINCT <-as.factor(data$PRECINCT)
data$JURISDICTION_CODE <- as.factor(data$JURISDICTION_CODE)
data$STATISTICAL_MURDER_FLAG <- as.factor(data$STATISTICAL_MURDER_FLAG)
data$VIC_AGE_GROUP <- as.factor(data$VIC_AGE_GROUP)
data$VIC_SEX <- as.factor(data$VIC_SEX)
data$VIC_RACE <- as.factor(data$VIC_RACE)
```
#Jurisdiction codes 0(Patrol), 1(Transit) and 2(Housing) represent 
#NYPD whilst codes 3 and more represent non NYPD jurisdictions

```{r}
#Check levels and missing value

levels(data$BORO)
levels(data$PRECINCT)
levels(data$JURISDICTION_CODE)
levels(data$STATISTICAL_MURDER_FLAG)
levels(data$VIC_AGE_GROUP)
levels(data$VIC_SEX)
levels(data$VIC_RACE)
```
```{r}
#Visualize the distribution of each variable

qplot(data$BORO)
qplot(data$PRECINCT)
qplot(data$STATISTICAL_MURDER_FLAG)
qplot(data$VIC_AGE_GROUP)
qplot(data$VIC_SEX)
qplot(data$VIC_RACE)
```
```{r}
#Date extraction

Sys.setlocale("LC_TIME","English_United States")
data$OCCUR_TIME = strptime(data$OCCUR_TIME, format = '%H:%M')
data = data %>%
  mutate(OCCUR_DATE = mdy(OCCUR_DATE)) %>%
  mutate(WEEKDAY = weekdays(OCCUR_DATE)) %>%
  mutate(HOUR = hour(OCCUR_TIME)) %>%
  mutate(YEAR = year(OCCUR_DATE))
```
```{r}
#Put only the necessary variables in the nypd table.

nypd <- data %>% select(YEAR,WEEKDAY,HOUR,BORO,JURISDICTION_CODE,
                        PRECINCT,STATISTICAL_MURDER_FLAG,
                        VIC_AGE_GROUP, VIC_SEX, VIC_RACE)

diagnose(nypd)
describe(nypd)
nypd <- na.omit(nypd)
```
```{r}
#Visualization of nypd

nypd %>%
  select(YEAR, BORO) %>%
  count(YEAR, BORO) %>%
  ggplot(aes(x = YEAR, y = n, group = BORO)) + geom_line(aes(color = BORO)) +
  geom_point(aes(color = BORO))

nypd %>%
  select(HOUR, BORO) %>%
  count(HOUR, BORO) %>%
  ggplot(aes(x = HOUR, y = n, group = BORO)) + geom_line(aes(color = BORO)) +
  geom_point(aes(color = BORO))

nypd %>%
  select(WEEKDAY, BORO) %>%
  count(WEEKDAY, BORO) %>%
  ggplot(aes(x = WEEKDAY, y = n, group = BORO)) + geom_line(aes(color = BORO)) +
  geom_point(aes(color = BORO))
```
```{r}
#mosaicplot

mosaicplot(STATISTICAL_MURDER_FLAG~WEEKDAY+HOUR,data=nypd,color=TRUE)
mosaicplot(STATISTICAL_MURDER_FLAG~VIC_AGE_GROUP+VIC_RACE,data=nypd,color=TRUE)
```
```{r}
#Creating an xgboost Classification Model

library(xgboost)
library(Matrix)
library(data.table)
library(MLmetrics)

levels(nypd$STATISTICAL_MURDER_FLAG) <- c(0,1)
head(nypd)
```
```{r}
xgb_sparse_matrix <- sparse.model.matrix(STATISTICAL_MURDER_FLAG~. -1, data = nypd)

# define train data set sampling index
train_index <- sample(1:nrow(xgb_sparse_matrix), 15000)

# Create train ,test data set , label data   
train_x <- xgb_sparse_matrix[train_index,]
test_x <- xgb_sparse_matrix[-train_index,]
train_y <- nypd[train_index,'STATISTICAL_MURDER_FLAG']
test_y <- nypd[-train_index,'STATISTICAL_MURDER_FLAG']

dtrain <- xgb.DMatrix(data = train_x, label= as.matrix(train_y))
dtest <- xgb.DMatrix(data = test_x, label= as.matrix(test_y))

```
```{r}
param <- list(max_depth = 100,
              eta = 0.001, 
              verbose = 0, 
              objective = "binary:logistic", 
              eval_metric = "auc")

xgb <- xgb.train(params = param,
                 data = dtrain, 
                 nrounds=3000, 
                 subsample = 0.7,
                 colsample_bytree = 0.6
)

train_y_pred <- predict(xgb, dtrain)
test_y_pred <- predict(xgb, dtest)

KS_Stat(train_y_pred,train_y)
KS_Stat(test_y_pred,test_y)

```
```{r}
# Feature importance

importance_matrix <- xgb.importance(dimnames(dtrain)[[2]], model = xgb)
importance_matrix
xgb.plot.importance(importance_matrix[1:10,])
```

#Conclusion

New York shooting accidents have decreased until 2019, but have been increasing rapidly since 2020.
The most accidents occur at 10 p.m. to 11 p.m.
Accidents occur the most on Sundays and then on Saturdays.
It occurs most frequently in the Brooklyn area.

As a result of checking feature importance in the XGBOOST classification model,

It is time and year that most affect death by gun. This seems to be due to the rapid increase in accidents last year and this year and the main occurrence at night.
In addition, there seems to be a high probability of death by gun due to the large number of black people.
